The Astropy Project

### 2017-10-20 main.tex
Update on Overleaf.

The package also provides the a histogram function, which is a generalization of \package{matplotlib}’s histogram function, to allow for more flexible specification of histogram bins.  The function provides several methods of automatically tuning the histogram bin size. It has a syntax identical to matplotlib’s plt.hist function, with the exception of the bins parameter, which allows specification of one of four different methods for automatic bin selection.

>>>>

The package also provides the a histogram function, which is a generalization of \package{matplotlib}’s histogram function, to allow for more flexible specification of histogram bins.  The function provides several methods of automatically tuning the histogram bin size. It has a syntax identical \package{matplotlib}’s histogram function, with the exception of the bins parameter, which allows specification of one of four different methods for automatic bin selection.
